Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-22 SIR_manuscript.tex
ref added

The basic reproduction number, $\Rnum$, was calculated by using the next generation matrix method developed by \cite{van2002reproduction}. $\Rnum$ is
\begin{equation}
\label{R0}
\Rnum= \frac{\beta}{\gamma} (1-\Delta), 
\end{equation}
where the term $\frac{\beta}{\gamma}$ is the classical basic reproduction number for a SIR model without testing and isolation \todo{ref?}, and $\Delta$ is the reduction parameter defined as follows.
\begin{equation}
\label{eq:Delta1}
\Delta= (A~ \theta\_w + B~ \theta\_c) / C,
\end{equation}
where
\begin{equation}
\begin{aligned}
\label{eq:abc}
A=& \gamma \Big( \big(\gamma(\omega+\gamma) + \omega p_I \hat F_I \big) \frac{S\_n^*}{N_0} + (\omega+\gamma) \hat F_I \Big),\\
B=& \omega p_I(\gamma \frac{S\_u^*}{N_0}+\omega)\hat F_I, \\ 
C=& (\omega+\gamma) \Big(\gamma(\omega+\gamma)+(\gamma+\omega p_I)\hat F_I\Big).
\end{aligned}
\end{equation}
Further details of derivation of $\Rnum$ are provided in the appendix section \ref{app:R0}.

>>>>

The basic reproduction number, $\Rnum$, was calculated by using the next generation matrix method developed by \cite{van2002reproduction}. $\Rnum$ is
\begin{equation}
\label{R0}
\Rnum= \frac{\beta}{\gamma} (1-\Delta), 
\end{equation}
where the term $\frac{\beta}{\gamma}$ is the classical basic reproduction number for a SIR model without testing and isolation (see, e.g., \cite{keeling2011modeling}), and $\Delta$ is the reduction parameter defined as follows.
\begin{equation}
\label{eq:Delta1}
\Delta= (A~ \theta\_w + B~ \theta\_c) / C,
\end{equation}
where
\begin{equation}
\begin{aligned}
\label{eq:abc}
A=& \gamma \Big( \big(\gamma(\omega+\gamma) + \omega p_I \hat F_I \big) \frac{S\_n^*}{N_0} + (\omega+\gamma) \hat F_I \Big),\\
B=& \omega p_I(\gamma \frac{S\_u^*}{N_0}+\omega)\hat F_I, \\ 
C=& (\omega+\gamma) \Big(\gamma(\omega+\gamma)+(\gamma+\omega p_I)\hat F_I\Big).
\end{aligned}
\end{equation}
Further details of derivation of $\Rnum$ are provided in the appendix section \ref{app:R0}.
